\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{SLIME SAT Solver\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}
%\thanks{Thanks to all supporters of http://www.peqnp.com projects.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Oscar Riveros}
Santiago, Chile \\
oscar.riveros@gmail.com
}

\maketitle

\begin{abstract}
A "on the fly" version of HESS algorithm for Multi-armed bandit style selection of rephasing, dual search algorithm, full remove of randomness on sequential and cloud version, based on SLIME sc2021 \cite{b1}.
\end{abstract}

\section{Introduction}
We create an on the fly version of HESS \cite{b1} algorithm, this allow an optimization of the rephasing states.
We create a dual search phase of the solver, one more simple and other more complex, this are called according if the VSIDS heuristic is running.
The DISTANCE heuristic is now parametric, on the experiments, DISTANCE work well with cryptographic instances, but not with generics.
For the cloud version the initial polarities are different for every node, on deterministic way, also the rank of the node is influencing on the execution.
On this version is added an optional parameter for sharing learnt clauses between nodes, alternate sharing clauses, and a filter for the size of learnt shared.
Several optimizations, and simplifications.
\section{Methods}

\subsection{HESS black-box algorithm}

HESS black-box algorithm \cite{b1} of º2 order to approximate values from an Oracle, In this case a "On The Fly" oracle as execution of SLIME and the sequence used to maximize the selection of rephase heuristics like Multi-armed bandit algorithm.

\subsection{HESS º2 order (On The Fly)}
\begin{itemize}
\item Create an initial sequence array $\rho(1, 2 \dots\ n)$
\item Repeat to a final state.
\item Set the current value to $\infty$.
\item Set $i$ to 0 and $j$ to 0.
\item increment $j$, if $j == n$ increment $i$ and put $j = 0$, if $i == n$, put $i = 0$ and $j = 0$. (two for loops)
\item invert the array from $min(i, j)$ to $max(i, j)$
\item Get $oracle()$ (call the search algorithm, and use the curren order of the array for select the bandit)
    \begin{enumerate}
        \item less than current value, reassign and retain the current assignment, and continue with next increment.
        \item if greater, change the array to original state, and continue with next increment.
        \item if equal, continue with next increment.
    \end{enumerate}
\item Continue with execution and repeat from step 2.
\end{itemize}

\subsection{Experimental Evaluation}

The default version of SLIME solve the 80\% of the entire Crypto Track 2021 (a set of cryptography instances) at 18000 seconds at www.starexec.org cluster.

\section{SLIME CLOUD}

Consist on a MPI implementation of SLIME where all nodes compete for the solution, can generate certificates for UNSAT.

\begin{thebibliography}{00}
\bibitem{b1} Balyo , T , Froleyks , N , Heule , M , Iser , M , Järvisalo , M & Suda , M (eds) 2021 , Proceedings of SAT Competition 2021 : Solver and Benchmark Descriptions . Department of Computer Science Report Series B , vol. B-2021-1 , Department of Computer Science, University of Helsinki , Helsinki .
\end{thebibliography}
\vspace{12pt}

\end{document}
